Model

### 2019-09-08 stats/model.Rmd
add model runs with more iterations

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
      }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

sem_know_model <- readRDS("../saves/sem_know_model_variant3_50k.rds")

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

@@

ggsave("../graphs/overview_variant_3_50k.png", width = 12, height = 4, scale = 1.2)

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 50000,
                        burn = 25000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 100)
)

@@

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_50k.rds")

>>>>

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
  //     slope: Math.pow(gaussianDrift({
  //       mu: globalLineParameters.slope, 
  //      sigma: itemVariability.slope, 
  //       width: 0.5
  //    }), 2)
      }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 50000,
                        burn = 25000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

sem_know_model <- readRDS("../saves/sem_know_model_variant2_50k.rds")

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_wrap(~item, nrow = 2)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

@@

ggsave("../graphs/overview_variant_3_100k.png", width = 12, height = 4, scale = 1.2)

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100000,
                        burn = 50000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 5000)
)

@@

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k.rds")
